\skills{
  \cvtag{Web Apps \& Mobile Apps Development}
  \smallskip

  \cvtag{UI Design}\cvtag{REST APIs}\cvtag{Web Scraping}

  \divider

  \cvtag{JavaScript}\cvtag{ReactJS}\cvtag{AngularJS}
  \smallskip

  \cvtag{Python}\cvtag{Django}\cvtag{Java}\cvtag{Android}
  \smallskip

  \cvtag{Git}\cvtag{Firebase}\cvtag{HTML}\cvtag{CSS}
}

\projects{
  \cvevent{UOS HUB}{Senior College Project}{}{}
  \begin{itemize}
    \item A website designed to unify all University of Sharjah websites in one place.
    \item It scrapes all student data and displays them in a user-friendly interface.
    \item Developed using a \emph{Python Django} back-end and an \emph{AngularJS} front-end.
  \end{itemize}

  \divider

  \cvevent{InstaBlock}{College Course Project}{}{}
  \begin{itemize}
    \item An Android app that instantly blocks the installation of other unwanted apps.
    \item It allows blocking installed apps, apps on Play Store or through custom filters.
    \item Written in \emph{Java} on \emph{Android Studio}, and uses \emph{Glide} for Internet queries.
  \end{itemize}

  \divider

  \cvevent{Interactive Resume}{Personal Website}{}{}
  \begin{itemize}
    \item Visually and interactively displays my projects, skills, information, and more.
    \item Developed using a \emph{ReactJS} front-end and linked with a \emph{Firebase} database.
  \end{itemize}
}

\publications{
  \smallskip

  \cvtitle{\large\printinfo{\fa{newspaper}}{Jornal Articles}}
  \begin{itemize}
    \item Talib, Manar Abu, Omar Einea, Qassim Nasir, Mohamad Fouzi Mowakeh, and Mohamed Eltawil. ``Enhancing computing studies in high schools: A systematic literature review \& UAE case study.'' \emph{Heliyon} 5, no. 2 (2019): e01235.
    \item Elnagar, Ashraf, Leena Lulu, and Omar Einea. ``An Annotated Huge Dataset for Standard and Colloquial Arabic Reviews for Subjective Sentiment Analysis.'' \emph{Procedia computer science} 142 (2018): 182-189.
  \end{itemize}

  \divider\medskip

  \cvtitle{\large\printinfo{\fa{users}}{Conference Proceedings}}
  \begin{itemize}
    \item Elnagar, Ashraf, Omar Einea, and Leena Lulu. ``Comparative study of sentiment classification for automated translated Latin reviews into Arabic.'' In \emph{2017 IEEE/ACS 14th International Conference on Computer Systems and Applications (AICCSA)}, pp. 443-448. IEEE, 2017.
    \item Elnagar, Ashraf, and Omar Einea. ``Brad 1.0: Book reviews in arabic dataset.'' \emph{In 2016 IEEE/ACS 13th International Conference of Computer Systems and Applications (AICCSA)}, pp. 1-8. IEEE, 2016.
  \end{itemize}
}

\referees{
  \cvtitle{Prof. Ashraf Elnagar}\par
  \printinfo{\fa{university}}{University of Sharjah}\smallskip

  \printinfo{\fa{pencil-ruler}}{Computer Science}\smallskip

  \printinfo{\fa{envelope}}{ashraf@sharjah.ac.ae}

  \divider

  \cvtitle{Dr. Manar Abu Talib}\par
  \printinfo{\fa{university}}{University of Sharjah}\smallskip

  \printinfo{\fa{pencil-ruler}}{Computer Science}\smallskip

  \printinfo{\fa{envelope}}{matalib@sharjah.ac.ae}

  \divider

  \cvtitle{Prof. Qassim Nasir}\par
  \printinfo{\fa{university}}{University of Sharjah}\smallskip

  \printinfo{\fa{pencil-ruler}}{Computer Engineering}\smallskip

  \printinfo{\fa{envelope}}{qassim@sharjah.ac.ae}
}