
\publications{
  \smallskip

  \cvtitle{\large\printinfo{\fa{newspaper}}{Journal Articles}}
  \begin{itemize}
    \item Omar Einea, Ashraf Elnagar, Ridhwan Al-Debsi. ``SANAD: Single-Label Arabic News Articles Dataset for Automatic Text Categorization'' \emph{Data in Brief}. Elsevier, 2019.
    \smallskip    
    \item Ashraf Elnagar, Ridhwan Al-Debsi, Omar Einea. ``Arabic text classification using deep learning models'' \emph{Information Processing \& Management} 57.1: 102121. Elsevier, 2020.
    \smallskip
    \item Ashraf Elnagar, Leena Lulu, and Omar Einea. ``An Annotated Huge Dataset for Standard and Colloquial Arabic Reviews for Subjective Sentiment Analysis.'' \emph{Procedia computer science} 142: 182-189. Elsevier, 2018.
    \smallskip
    \item Manar Abu Talib, Omar Einea, Qassim Nasir, Mohamad Fouzi Mowakeh,\\and Mohamed Eltawil. ``Enhancing computing studies in high schools: A systematic literature review \& UAE case study.'' \emph{Heliyon} 5, no. 2: e01235. Elsevier, 2019.
  \end{itemize}

  \divider\medskip

  \cvtitle{\large\printinfo{\fa{users}}{Conference Proceedings}}
  \begin{itemize}
    \item Omar Einea and Ashraf Elnagar. ``Predicting Semantic Textual Similarity of Arabic Question Pairs using Deep Learning.'' In \emph{2019 IEEE/ACS 16th International Conference on Computer Systems and Applications (AICCSA)}, pp. 1-5. IEEE, 2019.
    \smallskip
    \item Ashraf Elnagar, Omar Einea, and Ridhwan Al-Debsi. ``Automatic text tagging of Arabic news articles using ensemble deep learning models.'' In \emph{Proceedings of the 3rd International Conference on Natural Language and Speech Processing}, pp. 59-66. 2019.
    \smallskip
    \item Ashraf Elnagar, Omar Einea, and Leena Lulu. ``Comparative study of sentiment classification for automated translated Latin reviews into Arabic.'' In \emph{2017 IEEE/ACS 14th International Conference on Computer Systems and Applications (AICCSA)}, pp. 443-448. IEEE, 2017.
    \smallskip
    \item Ashraf Elnagar and Omar Einea. ``Brad 1.0: Book reviews in arabic dataset.'' \emph{In 2016 IEEE/ACS 13th International Conference of Computer Systems and Applications (AICCSA)}, pp. 1-8. IEEE, 2016.
    \smallskip
    \item Meriem Bettayeb, Omnia Abu Waraga, Manar Abu Talib, Qassim Nasir, and Omar Einea. ``IoT Testbed Security: Smart Socket and Smart Thermostat.'' In \emph{2019 IEEE Conference on Application, Information and Network Security (AINS)}, pp. 18-23. IEEE, 2019.
    \smallskip
    \item Ali AlZaabi, Manar Abi Talib, Ali Bou Nassif, Ali Sajwani, and Omar Einea.\\``A Systematic Literature Review on Machine Learning in Object Detection Security.'' In \emph{2020 IEEE 5th International Conference on Computing Communication and Automation (ICCCA)}, pp. 136-139. IEEE, 2020.
  \end{itemize}
}

\referees{
  \cvtitle{Prof. Ashraf Elnagar}\par
  \printinfo{\fa{university}}{University of Sharjah}\smallskip

  \printinfo{\fa{pencil-ruler}}{Computer Science}\smallskip
  
  \printinfo{\fa{envelope}}{ashraf@sharjah.ac.ae}

  \divider

  \cvtitle{Ridhwan Al-Debsi}\par
  \printinfo{\fa{university}}{Saal ai}\smallskip
  
  \printinfo{\fa{pencil-ruler}}{Machine Learning Engineer}\smallskip
  
  \printinfo{\fa{envelope}}{ridhwan@saal.ai}

  \divider

  \cvtitle{Dr. Manar Abu Talib}\par
  \printinfo{\fa{university}}{University of Sharjah}\smallskip
  
  \printinfo{\fa{pencil-ruler}}{Computer Science}\smallskip
  
  \printinfo{\fa{envelope}}{matalib@sharjah.ac.ae}

  \divider

  \cvtitle{Prof. Qassim Nasir}\par
  \printinfo{\fa{university}}{University of Sharjah}\smallskip
  
  \printinfo{\fa{pencil-ruler}}{Computer Engineering}\smallskip
  
  \printinfo{\fa{envelope}}{qassim@sharjah.ac.ae}

  \divider

  \cvtitle{Dr. Ali Bou Nassif}\par
  \printinfo{\fa{university}}{University of Sharjah}\smallskip
  
  \printinfo{\fa{pencil-ruler}}{Computer Engineering}\smallskip
  
  \printinfo{\fa{envelope}}{anassif@sharjah.ac.ae}
}